Rationality, Evolution \& the Environment

### 2015-05-21 paper/paper.tex
outline tweaks

\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
  deviations of human decision making from the classical ideal: choice behavior evolved to be an
  ``ecologically rational'', near-optimal adaptation to the environment \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}

@@

\begin{itemize}
\item given previous results, there are really only two kinds of types to look at:
  \begin{enumerate}
  \item (prob., veridical), (prob., regret) and (non-prob., regret) \\ 
    \textcolor{gray}{[all choice-equivalent in this case]}
  \item (non-prob., veridical)
  \end{enumerate}
\item RESULT: the former class ``dominates'' the latter (our main result, Proposition 1 from
  TARK paper)
\item this means that evolutionary dynamics would weed out (non-prob., regret); every
  population composition between the remaining three is neutrally stable; all interior
  trajectories (of the replicator dynamic) converge to these
\item further results (from TARK):
  \begin{itemize}
  \item component-wise mutation: abundance of regret types
  \item exogenously given correlated epistemic types: regret types dominate
  \item exogenously given uncorrelated epistemic types: regret types dominate
  \end{itemize}
\todo[inline]{work out these additional results more carefully; present graphs if possible}
\end{itemize}

>>>>

\item We argue that this ``meta-evolutionary'' approach could eventually help explain attested
  deviations of human decision making from the classical ideal: choice behavior evolved to be
  an ``ecologically rational'', near-optimal adaptation to the environment
  \citep{Anderson1990:The-Adaptive-Ch,Anderson1991:Is-human-cognit,GigerenzerGoldstein1996:Reasoning-the-F,ChaterOaksford2000:The-Rational-An}. This
  is inline with recent aspirations to provide an evolutionary rationale for decision making
  processes
  \citep[e.g.][]{HammersteinStevens2012:Six-Reasons-for,FawcettHamblin2013:Exposing-the-be}. Here,
  we seek to contribute to the formal machinery, an extension of evolutionary game theory, that
  allows to capture statistical properties of the environment
  \citep[cf.][]{McNamara2013:Towards-a-Riche}.

@@

\begin{itemize}
\item given previous results, there are really only two kinds of types to look at:
  \begin{enumerate}
  \item (prob., veridical), (prob., regret) and (non-prob., regret) \\ 
    \textcolor{gray}{[all choice-equivalent in this case]}
  \item (non-prob., veridical)
  \end{enumerate}
\item RESULT: the former class ``dominates'' the latter (our main result, Proposition 1 from
  TARK paper)
\item this means that evolutionary dynamics would weed out (non-prob., regret); every
  population composition between the remaining three is neutrally stable; all interior
  trajectories (of the replicator dynamic) converge to these
\item further results (from TARK):
  \begin{itemize}
  \item component-wise mutation: abundance of regret types
    \begin{itemize}
    \item different evolutionary paths despite the same behavior (contra the ``behavioral
      gambit'' \citep{FawcettHamblin2013:Exposing-the-be})
    \end{itemize}
  \item exogenously given correlated epistemic types: regret types dominate
  \item exogenously given uncorrelated epistemic types: regret types dominate
  \end{itemize}
\todo[inline]{work out these additional results more carefully; present graphs if possible}
\end{itemize}
